---
title: "1Homework-Function-413"
author: "Emmenta Janneh & Alphonso J. Saiewanne"
date: "2024-01-29"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(readr)
library(dplyr)
library(ggplot2)
```


1. Write a function that will find the sum of the natural log, the common log and a log of base 2 for any given positive number. Use your function to find answers for the first five even integers.  Show all details and structure of your function.  You should get five answers. The first two answers are 1.994177 and 3.988354. (Your output should show the other three)

- Menthod 1

```{r}
# Function to calculate the sum of logarithms
log_sum <- function(number) {
  # Check if the number is positive
  if (number <= 0) {
    return("Input must be a positive number.")
  }

  # Calculate logarithms
  natural_log <- log(number)
  common_log <- log10(number)
  log_base_2 <- log2(number)

  # Calculate the sum
  log_sum_result <- natural_log + common_log + log_base_2

  # Return the result
  return(log_sum_result)
}

# Calculate the sum for the first five even integers
even_integers <- c(2, 4, 6, 8, 10)

# Apply the function to each even integer and print the results
for (num in even_integers) {
  result <- log_sum(num)
  cat("For", num, ":", result, "\n")
}
  
```

- Method 2

```{r}
log_sum <- function(num) {
  natural_log <- log(num)
  common_log <- log10(num)
  base2_log <- log2(num)
  total <- natural_log + common_log + base2_log
  return(total)
}
```


- Now, I can use this function to find the sum for the first five even integers:

```{r}
num_1 <- 2
num_2 <- 4
num_3 <- 6
num_4 <- 8
num_5 <- 10

sum_1 <- log_sum(num_1)
sum_2 <- log_sum(num_2)
sum_3 <- log_sum(num_3)
sum_4 <- log_sum(num_4)
sum_5 <- log_sum(num_5)

cat("The first two answers are:", sum_1, "and", sum_2, "\n")
cat("The other three answers are:", sum_3, ",", sum_4, "and", sum_5)
```


2. Use the if-else structure to print the statement "This is a big number" if the square of a value is greater than or equal to 100 and the following statement is printed if the square of the number is less than 100, "This is not a big number”. Use and show values of assignment and if-else structures that will output both statements.


- In this example, I have assigned the value **`10`** to the variable **`num`**. We then use the **`if-else`** structure to check if the square of **`num`** is greater than or equal to **100**. If it is, the statement **"This is a big number"** is printed. Otherwise, the statement **"This is not a big number"** is printed.

```{r}
num <- 10

if(num^2 >= 100) {
  print("This is a big number")
} else {
  print("This is not a big number")
}
```


In this example, I have assigned the value **`9`** to the variable **`num`**. We then use the **`if-else`** structure to check if the square of **`num`** is greater than or equal to **100**. If it is, the statement **"This is a big number"** is printed. Otherwise, the statement **"This is not a big number"** is printed.

```{r}
num <- 9

if(num^2 >= 100) {
  print("This is a big number")
} else {
  print("This is not a big number")
}
```


3. For the following if-else-if coding structure, make an adjustment so that it prints "Team A won"
team_A <- 2 # Number of goals scored by Team A
team_B <- 2# Number of goals scored by Team B

```{r}
team_A <- 2 # Number of goals scored by Team A
team_B <- 1 # Number of goals scored by Team B

if (team_A > team_B) {
  print("Team A won")
} else if (team_A < team_B) {
  print("Team B won")
} else {
  print("Team A & B tied")
}
```

4. Write an if- else if- else sequence of commands that will output the following statements and appropriate output; If a value is divisible by 3 and 5 the output statement is "divisible by Three and Five", If a value is divisible by 3 and 4, the output statement is "divisible by Three and Four, If a value is a number that does not fall into either category, the output statement should be  "neither".Use your function to show output statements for values 16, 45, and 24.


```{r}
check_divisibility <- function(value) {
  if (value %% 3 == 0 && value %% 5 == 0) {
    print("Divisible by Three and Five")
  } else if (value %% 3 == 0 && value %% 4 == 0) {
    print("Divisible by Three and Four")
  } else {
    print("Neither")
  }
}

# Test the function with values 16, 45, and 24
check_divisibility(16)
check_divisibility(45)
check_divisibility(24)


```

5. Use piping and a dplyr command show and use R code to produce the following modified mpg data table that contains only quantitative variables.

- Now use the “special loop coding chunk”, illustrated in class, to produce the variance for all variables of the modified data table.


```{r}
## Assuming mpg is your data frame
library(dplyr)

# Filter only specific columns
mpg_filtered <- mpg %>%
  select(displ, cyl, cty, hwy)

# Calculate the variance for each variable
variances <- sapply(mpg_filtered, var)

# Print the modified data table and variances
print(mpg_filtered)
print(variances)
```


6. Construct a for loop (as illustrated in the notes) that will produce the difference between the cube and the square for each prime number between 10 and 30.  (There are 6 answers. The first answer is 1210, your for loop coding should produce the other five answers)

```{r}
# Function to check if a number is prime
is_prime <- function(n) {
  if (n <= 1) return(FALSE)
  if (n == 2) return(TRUE)
  if (any(n %% 2:(floor(sqrt(n))) == 0)) return(FALSE)
  return(TRUE)
}

# Initialize a vector to store the results
results <- numeric(0)

# Iterate through prime numbers between 10 and 30
for (i in 10:30) {
  if (is_prime(i)) {
    # Calculate the difference between cube and square
    result <- i^3 - i^2
    # Append result to the vector
    results <- c(results, result)
  }
}

# Print the results
print(results)
```
```

# Example 7

- (Let's write a function that will test for# divisibility)

# Is 125 divisible by 3?

# Method 1

